Learning CNN filters from user-drawn image markers for coconut-tree image classification

### 2020-07-23 main.tex
Updates from Overleaf

@@

     \node (sup) [steps, right=2em of features] {Supervised\\Learning};

@@

\textcolor{red}{
The experiments have been designed to evaluate the following hypotheses about FLIM.
\begin{enumerate}
 \item[(H1)]  FLIM can produce competitive image feature extractors from user-drawn markers in a few images selected per class from a training set. 
\item[(H2)]  For a given network architecture, FLIM can provide better classification results than those obtained by training that network with backpropagation.
\item[(H3)] Its feature extractor remains competitive independently of the training set size. 
\item[(H4)] User-drawn markers on a higher number of selected images from the training set can improve image feature extraction.
\end{enumerate}
}

>>>>

     \node (imgs) [fit={($(img1.north west)+(-0.45,0.1)$) ($(img3.south east)+(0.45,-0.1)$)}, inner sep=0pt, draw=none, rounded corners, very thick, label = {[label distance = 0.1em]below:{Testing set}}] {};
     %----------------------------------

@@

     \node (sup) [steps, right=2em of features] {Classification};

@@

\textcolor{red}{
The experiments have been designed to evaluate the following hypotheses about FLIM.
\begin{enumerate}
 \item[(H1)]  FLIM can produce competitive image feature extractors from user-drawn markers in a few images selected per class from a training set. 
\item[(H2)]  For a given network architecture, FLIM can provide better classification results than those obtained by training the same architecture with backpropagation.
\item[(H3)] Its feature extractor remains competitive independently of the training set size. 
\item[(H4)] User-drawn markers on a higher number of selected images from the training set can improve feature extraction.
\end{enumerate}
}
